Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-17 mu/article/article.tex
Changing working station.

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk systems. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the THz radiation and reaching a
spin velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the near infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
%

@@

an incoming energy beam from 0.0\,eV to 0.2\,eV in the THz radiation range,
where the absolute maximum of the $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$
response is obtained and the second for an energy range from 1.80\,eV to
2.1\,eV, corresponding to the THz and visible radiation, where two local maxima
are found.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
% %% Description of ALT |V_{s^z}| 3D
% %%%%%%%%%%%%%%%%%
\textbf{Alt structure}

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the THz radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} using different polarization angle $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.

>>>>

In figure \ref{fig:vab-str-comp} we present a comparison of the most intense
responses resulting from evaluate the Eq. \eqref{eq:vab} for the \emph{alt} and
\emph{up} 2D structures vs. CdSe and GaAs bulk systems. As we can see from
this figure the most intense response corresponds to the \emph{up} structure
centered at 0.088\,eV corresponding to the THz radiation and reaching a
spin velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures.
%

@@

an incoming energy beam from 0.0\,eV to 0.2\,eV which inlude the THz and the Mid
Infrared (MIR) range, where the absolute maximum of the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained and the
second for an energy range from 1.80\,eV to 2.1\,eV, corresponding to visible
radiation, where two local maxima are found.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV  &  1.80 ev - 2.1 ev
% %% Description of ALT |V_{s^z}| 3D
% %%%%%%%%%%%%%%%%%

\textbf{Alt structure}

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
polarization angle $\alpha$ for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.
